Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
more work on results

Our default resolution puts $\sim 100$ zones vertically in the
``cool'' \MarginPar{double check} model atmosphere height.  To
understand the effects of resolution, we also perform a run with one
fewer level, giving at $20~\mbox{cm}$ resolution overall.  Figure~\ref{fig:10_10_lowres}
shows the fields at 20~ms.

@@

@@

\AssignTo{Kiran}

@@

\subsection{Boosting}

\AssignTo{Kiran, Mike}

To meet reasonable timescales, we boosted the microphysical inputs to
the flame to result in a faster flame.  Here we look at the effect of
this choice.

\begin{figure}[h]
\centering
\plotone{flame_wave_boost_5_5_slice}
\caption{\label{fig:5_5_overview} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 5/5 simulation.}
\end{figure}

@@

\subsection{Rotation Rate}

\AssignTo{Mike, Kiran}

We also try a rotation period of $P_\mathrm{rot} \sim 10^{-3}~\mathrm{s}$.

\subsection{Reaction Network}

\AssignTo{Mike, Kiran}

We look at iso7 instead of aprox13

>>>>

Our default resolution puts $\sim 80$ zones vertically in the
``cool'' \MarginPar{double check} model atmosphere height.  To
understand the effects of resolution, we also perform a run with one
fewer level, giving at $20~\mbox{cm}$ resolution overall (this is our
10/10-lores run).  Figure~\ref{fig:10_10_lowres} shows the fields at
20~ms.  The structure is largely the same as the 10/10 run, with
largely the same flame shape and position, and the same structure in
the energy generation rate.  Since we do not have a jump in refinement
right below the atmosphere, we don't see the strong diffusive effect
there, but we do see some cooling in the \isot{Ni}{56} region.  This
is likely a resolution effect, again due to the strong gradient in
temperature at the base of the atmosphere.

@@

\subsection{Effects of our Approximations}

The results above all used a boosting of 10/10.  To see how the
results are sensitivity to our boosting we ran a simulation with a
boosting of 5/5.  This is shown in Figure~\ref{fig:5_5_overview}.  The
results look qualitatively the same---a laterally propagating flame
develops that is lifted off of the bottom of the fuel layer.  The
flame has not moved out as far as in the 10/10 simulation, simply
because there is less energy release, but we expect that if we were to
run this out twice as long, the flame would have advanced to the
position seen in our 10/10 runs.  The good agreement in the structure
of the flame seen with the lower boosting gives us confidence that the
overall aspects of the flame structure and acceleration we are seeing
are robust to the approximations we make.

\begin{figure}[h]
\centering
\plotone{flame_wave_boost_5_5_slice}
\caption{\label{fig:5_5_overview} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 5/5 simulation at 20~ms.}
\end{figure}

We can also look at the

@@

@@

{\color{red} Should say qualitatively what the plot shows}

@@
